### 2020-06-22 TCS_version/01-introduction.tex
aggiunta biblio

As we have remarked, in our translation, Reaction Systems 
get the ability to interact between them in a synchronized manner. 
This interaction is not foreseen in
the basic RS framework, as it can only happen with the context.
By exploiting recursion, the kind of interactions which can be 
defined can be complex and expressive.
Example~\ref{ex:twoRS} and more in general the discussion in 
Section~\ref{subsec:comRS}
%~\ref{sec:discussion}
 show that 
the interaction between RSs can help to model new scenarios.

>>>>

As we have remarked, in our translation, Reaction Systems 
get the ability to interact between them in a synchronized manner. 
This interaction is not foreseen in
the basic RS framework, as it can only happen with the context.
{\color{red}The proposed network of reaction systems~\cite{BLR20} allows
any reaction system in the network to receive entities 
produced from its neighbors (that will represent its context), with the hypothesis that  
reaction systems without neighbors will receive no entities 
from the context. 
}
By exploiting recursion, the kind of interactions which can be 
defined can be complex and expressive.
Example~\ref{ex:twoRS} and more in general the discussion in 
Section~\ref{subsec:comRS}
%~\ref{sec:discussion}
 show that 
the interaction between RSs can help to model new scenarios.
